Simulation study in rectangular domain

### 2024-04-28 R/simulation_study/simulation_study_rect.Rmd
update simulation study

```{r libraries}
#seed for reproducibility 
set.seed(1)

@@

```{r global variables}
#number of batch
N_BATCH=10

@@

#degree of freedom in tensor splines
SP_DF=5

@@

```{r}
plot_spline_omega
```

```{r}
plot_basis2

@@

```{r}
plot_basis3
saveWidget(plot_basis3, file ="spline_basis3_omega_rect.html")
```

```{r}
plot_basis4
saveWidget(plot_basis4, file ="spline_basis4_omega_rect.html")
```

@@

crcvm_rect_hf_ne1<- foreach(i=1:N_BATCH,.packages=c("smoothSDE")) %do% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,ExpShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H_hf))
  m$fit(method="BFGS")
  m 
}

@@

crcvm_rect_hf_ne2<- foreach(i=1:N_BATCH,.packages=c("smoothSDE")) %do% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H_hf))
  m$fit(method="BFGS")
  m 
}

>>>>

```{r libraries}
#seed for reproducibility 
set.seed(42)

@@

```{r global variables}
#number of batch
N_BATCH=100

@@

#degree of freedom in tensor splines
SP_DF=3

@@

```{r plot spline omega}
plot_spline_omega
```

```{r plot basis2}
plot_basis2

@@

```{r plot basis3}
plot_basis3
saveWidget(plot_basis3, file ="spline_basis3_omega_rect.html")
```

```{r plot basis4}
plot_basis4
saveWidget(plot_basis4, file ="spline_basis4_omega_rect.html")
```

@@

crcvm_rect_hf_ne1<- foreach(k=1:N_BATCH,.packages=c("smoothSDE")) %do% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,ExpShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H_hf))
  m$fit(method="BFGS")
  m 
}

@@

crcvm_rect_hf_ne2<- foreach(k=1:N_BATCH,.packages=c("smoothSDE")) %do% {
  #estimation with tensor splines
  formulas <- list(mu1=~1,mu2=~1,tau=~s(ID,bs="re"),
                 nu=~s(ID,bs="re"),omega=~te(theta,DistanceShore,k=SP_DF,bs="cs"))
  par0 <- c(0,0,1,1,0)
  m <- SDE$new(formulas = formulas,data = data_rect_hf_ne[[paste("BATCH",k,sep="")]],type = "RACVM",
                      response = c("y1","y2"),par0 = par0,fixpar=c("mu1","mu2"),
                      other_data=list("H"=H_hf))
  m$fit(method="BFGS")
  m 
}
